HERMES : Hybrid ERror-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2021-12-02 hermes_paper/hermes_paper.tex
Correction section 2

\section{Hybrid model with external signals}
\label{sec:hybrid}
%We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model with seasonal component and a global RNN. We use a per time series statistical model to learn local behaviour and to normalize sequences before feeding them to the neural network.
%We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model with seasonal component and a global neural network framework composed of two RNN. We use a per time series statistical model to learn local behaviour, to normalize sequences by removing trends and seasonality,  and to compute a first forecast. Then, we use two recurrent neural networks and weak signals to correct, if needed, the predictions provided by the first collection of parametric models.
We introduce a new hybrid approach for time series forecasting  composed of two parts: a collection of per-time-series parametric models, the predictors, and a global error-corrector neural network train on all the time series, the corrector. We use  per-time-series parametric models to learn local behaviour, to normalize sequences by removing trends and seasonality,  and to compute a first forecast. Then, gathering information of the first predictions and external variables, we use a recurrent neural networks to correct the predictions provided by the first collection of per-time-series models.

@@

During the M4 competition, the hybrid model of \cite{smyl2020hybrid} was based on a multiplicative exponential smoothing model as the time-series-specific predictor. However, on sporadic time series, this choice could lead to poor result and instability. In our approach, we decided to go deeper and provide a general framework able to deal with any kind of per-time-series models. In Section~\ref{sec:exp}, we present two versions of our framework. The first one use an  exponential smoothing as reference similar to \cite{smyl2020hybrid} and the second one use a TBATS model \cite{doi:10.1198/jasa.2011.tm09771} which provides better results. The main complexity is in the next stage: training a global RNN corrector to improve the per-time-series statistical models when the parametric models start showing weaknesses.

As weakness to correct, we detected and defined two main forms for a univariate parametric forecast as define above. The first one is a weakness of definition, when the model is not well define for its forecasting task. For instance, an additive model provide good predictions on time series with additive seasonality but show difficulties with multiplicative one. The second form, harder to detect and correct, is the weakness of information. For non stationary time series, huge changes of behaviours are not always predictable using the past of the sequence. In somes cases, these changes depend on external variables not considered by univariate parametric models. The difficulty is that we mainly unknow the exact influence of external variables on the main signal. It is on this point that our new hybrid framework shows its true potential: introduce a global RNN train on all the time series and able to consider and leverage external signals.\textcolor{red}{Plutot dire ici que l'on souhaite corriger des erreurs specifiques: et introduire les types de trends mal predites que l'on souhaite corriger.}
% Indeed, depending on time series, some family of parametric models can achieve really heterogeneous level of accuracy. 
%For all $1\leqslant n \leqslant N$, let $\Theta^n = \{\alpha^n, \gamma^n, \lvl^n_0, \{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}\}$ be the parameters of the $n$-th sequence with $\lsmooth^n$ and $\ssmooth^n$ the positive smoothing parameters, $\lvl^n_0$ the first level term and $\{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}$ the $m$ first seasonality terms. Given the sequence $\fullts^n$ and the parameters $\Theta^n$ , the two components  $\fulllvl^n$ and $\fullseas^n$ are computed as follow :
%We initialize the first level with $\lvl^n_{0} = \sum_{t = 1}^m \ts^n_{t}/m$ \textcolor{red}{issue with the time index ?} and, for all $1\leqslant n \leqslant N$ and $1\leqslant t \leqslant T$,
%\begin{align*}
    %\lvl^n_{t} &= \lsmooth^n (\ts^n_t - \seas^n_{t-m}) + (1- \lsmooth^n)\lvl^n_{t-1}\,, \\
    %\seas^n_t &= \ssmooth^n (\ts^n_t - \lvl^n_{t-1}) + (1 - \ssmooth^n)\seas^n_{t-1}\,. 
%\end{align*}

>>>>

\section{Hybrid model with external signals}
\label{sec:hybrid}
%We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model with seasonal component and a global RNN. We use a per time series statistical model to learn local behaviour and to normalize sequences before feeding them to the neural network.
%We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model with seasonal component and a global neural network framework composed of two RNN. We use a per time series statistical model to learn local behaviour, to normalize sequences by removing trends and seasonality,  and to compute a first forecast. Then, we use two recurrent neural networks and weak signals to correct, if needed, the predictions provided by the first collection of parametric models.
We introduce a new hybrid approach for time series forecasting  composed of two parts: a collection of per-time-series parametric models, the predictors, and a global error-corrector neural network train on all time series, the corrector. We use  per-time-series parametric models to learn local behaviour, to normalize sequences by removing trends and seasonality,  and to compute a first forecast. Then, gathering information of the first predictions and external variables, we use a recurrent neural networks to correct the predictions provided by the first collection of per-time-series models.

@@

During the M4 competition, the hybrid model of \cite{smyl2020hybrid} was based on a multiplicative exponential smoothing model as the time-series-specific predictor. However, on sporadic time series, this choice leads to poor result and instability. In this paper, we provide a general framework able to deal with any kind of per-time-series models. In Section~\ref{sec:exp}, we present two versions of our framework. The first one use an  exponential smoothing as reference similar to the baseline \cite{smyl2020hybrid} and the second one use a TBATS model \cite{doi:10.1198/jasa.2011.tm09771} which provides better results as this parametric model includes  Fourier representations with time varying coefficients, and ARMA error correction. %The main complexity is in the next stage: training a global RNN corrector to improve the per-time-series statistical models when the parametric models start showing weaknesses.

In the specific application of fashion trends prediction, we detected and defined two main forms of standard weaknesses for a univariate parametric forecast as defined above. The first one is a weakness of definition, when the model is not well defined for its forecasting task. For instance, an additive model provide good predictions on time series with additive seasonality but show difficulties with multiplicative one. The second form, harder to detect and correct, is the weakness of information. For non stationary time series, huge changes of behaviours are not always predictable using the past of the sequence. In somes cases, these changes depend on external variables not considered by univariate parametric models. The difficulty is that we mainly unknow the exact influence of external variables on the main signal. It is on this point that our new hybrid framework shows its true potential: introduce a global RNN trained on all the time series and able to consider and leverage external signals.

\medskip

\textcolor{red}{Ajouter ici une figure avec une ou deux series temporelles mal predites par le modele statistique et bien corrigees par le RNN pour illustrer le potentiel.}
% Indeed, depending on time series, some family of parametric models can achieve really heterogeneous level of accuracy. 
%For all $1\leqslant n \leqslant N$, let $\Theta^n = \{\alpha^n, \gamma^n, \lvl^n_0, \{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}\}$ be the parameters of the $n$-th sequence with $\lsmooth^n$ and $\ssmooth^n$ the positive smoothing parameters, $\lvl^n_0$ the first level term and $\{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}$ the $m$ first seasonality terms. Given the sequence $\fullts^n$ and the parameters $\Theta^n$ , the two components  $\fulllvl^n$ and $\fullseas^n$ are computed as follow :
%We initialize the first level with $\lvl^n_{0} = \sum_{t = 1}^m \ts^n_{t}/m$ \textcolor{red}{issue with the time index ?} and, for all $1\leqslant n \leqslant N$ and $1\leqslant t \leqslant T$,
%\begin{align*}
    %\lvl^n_{t} &= \lsmooth^n (\ts^n_t - \seas^n_{t-m}) + (1- \lsmooth^n)\lvl^n_{t-1}\,, \\
    %\seas^n_t &= \ssmooth^n (\ts^n_t - \lvl^n_{t-1}) + (1 - \ssmooth^n)\seas^n_{t-1}\,. 
%\end{align*}
